\section{Evaluation}
PIPE 5 has significant improvement gains in the structuring of its classes and packages. Stan4J now reports only two tangles of size 11 and 2 opposed to the four tangles in PIPE 4 of size 18, 10, 7 and 5. This reduction in tangles reduces the overall tangle metrics for the repositories as seen in \cref{tbl:tangle_results} and the tangle graphs are visualised in \cref{fig:tangle_results}. 

By analysing all the repositories PIPE 5 was split into we can see that the previous count of \num{12904} reported issues for PIPE 4 has been considerably reduced to a total of \num{937} issues. The break down of quality issues across repositories can be seen in \cref{tbl:pipe5_qaplug}. Furthermore Stan4J reported that the project size has reduced by a third from around \num{66000} lines of code to \num{22000}.

Our new sequential state space exploration algorithm  yields increasing speedups compared to PIPE 4 for small state spaces as shown in \cref{tbl:pipe5_vs_pipe4_sequential}. Interestingly the algorithm for the sequential exploration does not differ from that of PIPE 4, the speedup comes from advanced data structure usage, memoization and other optimisation techniques.

To investigate the scalability of our parallel algorithm we analysed the new sequential and parallel algorithms against each other using a machine with a 3.40Ghz quad-core i7 processor. \cref{fig:scalability} shows that whilst the speedup from 2 to 4 virtual cores is promising at around 60\%, we do not get such good results from running the algorithm with 8 virtual cores. On profiling we found that the bottleneck in our algorithm is due to a concurrent queue of state to process containing duplicate items. Unfortunately there is no implementation of a concurrent queue in Java that does not allow duplicates and so further work should be explored in this area to overcome this problem.

Nevertheless in order to put into perspective the speedup gained by our new parallel algorithm using 100 states per thread and 8 virtual-cores we compared the run-times of a 4096 state Petri net with this algorithm and PIPE 4. Whilst PIPE 4 explores the state space in 9.37 minutes, our new algorithm can explore it in 2.65 seconds which amounts to an incredible 211x speedup. Moreover our new algorithm can solve a Petri net with \num{1099999} states in 5.77 minutes which is faster than the time taken to solve the 4096 state Petri net in PIPE 4!
\input{eval/tangles_table}
\input{eval/tangles}
\input{eval/qaplug_table}
\input{eval/speedup_table.tex}
\input{eval/labs_state_space.tex}

